Analysis of Turkey's Trade with Selected Countries

### 2018-12-20 Draft/PresentationDraft.Rmd
.

```{r, fig.align='center', fig.height=5, fig.width=10}
summarytableRussianIm <- import_jTableMELTED %>%
  filter(Country=="Russian") %>%
  group_by(X__2, year) %>%
  summarise(ImportValue=sum(Values)) %>%
  arrange(X__2, year) %>%
  mutate(ImpPercChngYoY = (ImportValue - lag(ImportValue))/lag(ImportValue)*100) %>%
  mutate(ImpChngYoy=((ImportValue - lag(ImportValue)))) %>%
  filter(year!=2013)

@@

ggplot(summarytableRussianIm, aes(x=substr(X__2, start = 1, stop = 30))) +
  geom_point(aes(y=ImpChngYoy, color=year), size=4) + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  facet_grid (~year) +
  facet_grid(rows = vars(year)) +
  labs(
       x="Product Group",
       y="Change in Import Value",
       Color=c("Year"))
```

Discover more with ***[Shiny](https://groupfour.shinyapps.io/tradeOrg)***

>>>>

```{r, fig.align='center', fig.height=4.5, fig.width=10}
summarytableRussianIm <- import_jTableMELTED %>%
  filter(Country=="Russian") %>%
  group_by(X__2, year) %>%
  summarise(ImportValue=sum(Values)) %>%
  arrange(X__2, year) %>%
  mutate(ImpPercChngYoY = (ImportValue - lag(ImportValue))/lag(ImportValue)*100) %>%
  mutate(ImpChngYoy=((ImportValue - lag(ImportValue)))) %>%
  filter(year!=2013)

@@

ggplot(summarytableRussianIm, aes(x=substr(X__2, start = 1, stop = 30))) +
  geom_point(aes(y=ImpChngYoy, color=year), size=4) + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  facet_grid (~year) +
  facet_grid(rows = vars(year)) +
  labs(
       x="Product Group",
       y="Change in Import Value",
       Color=c("Year"))
```
<div class="centered" class="red2">
Discover more with ***[Shiny](https://groupfour.shinyapps.io/tradeOrg)***
</div>

## Analysis of Trade Deficit by Countries and Years

```{r, fig.align='center'}
export_Product_Group <- export_jTableMELTED%>%
group_by(Country,PcodeTwo,X__2,year)%>%
summarize(Quantity = sum(Quantity), Values = sum(Values))%>%
rename(Product_Group_Code =PcodeTwo, Product_Group_Name = X__2,Export_Quantity = Quantity,Export_Value =Values)

import_Product_Group <- import_jTableMELTED%>%
group_by(Country,PcodeTwo,X__2,year)%>%
summarize(Quantity = sum(Quantity), Values = sum(Values))%>%
rename(Product_Group_Code =PcodeTwo, Product_Group_Name = X__2,Import_Quantity = Quantity,Import_Value =Values)

Export_Import_JTable <- export_Product_Group %>%
  full_join(import_Product_Group,by=c("Country","Product_Group_Code","Product_Group_Name","year")) %>%
mutate(Import_Quantity = replace(Import_Quantity, is.na(Import_Quantity),0),
        Export_Quantity = replace(Export_Quantity, is.na(Export_Quantity),0))%>%
select(Country,Product_Group_Code,Product_Group_Name,year,Export_Quantity,Import_Quantity,Export_Value,Import_Value)

####Net Value By Country###
Net_Value_By_Country <- Export_Import_JTable %>%
group_by(Country,year)%>%
summarize (Export_Value = sum(Export_Value), Import_Value = sum(Import_Value), 
           Net_Value = sum(Export_Value - Import_Value),Net_value_K = round((sum(Export_Value - Import_Value)/1000),digits=0))

# Total Net Value fiiled with Country on the basis of Year #
ggplot(Net_Value_By_Country, aes(x=year, y=Net_value_K)) + 
  geom_bar(stat='identity', aes(fill=Country), width=.6,position = position_stack(reverse = TRUE))  +
  labs(title= "Total Net Values") + 
  coord_flip()+
  theme(legend.position = "top")
```
